---
title: "Flanker"
author: "Maria Polychronidou"
date: "3/3/2022"
output:
  word_document:
    toc: yes
  html_document:
    toc: yes
    code_folding: hide
    toc_float:
      collapsed: no
      smooth_scroll: yes
    number_sections: yes
  pdf_document:
    toc: yes
---


```{r}
library(readr)
library(tidyverse)
```


```{r}
Polym001_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym001_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym002_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym002_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym003_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym003_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym004_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym004_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym005_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym005_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym006_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym006_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym007_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym007_Flanker task.txt", 
    delim = "\t", escape_double = FALSE,
    trim_ws = TRUE)
Polym008_Flanker_task <-read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym008_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym009_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym009_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym010_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym010_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym011_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym011_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym012_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym012_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym013_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym013_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym014_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym014_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym015_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym015_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym016_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym016_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym017_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym017_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym018_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym018_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym019_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym019_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym020_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym020_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym021_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym021_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym022_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym022_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym023_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym023_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym024_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym024_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym025_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym025_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym026_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym026_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym027_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym027_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym028_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym028_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym029_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym029_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
Polym030_Flanker_task <- read_delim("C:/Users/polyc/Desktop/THESIS/ANALYSIS/COGNITIVE TASKS/Flanker xlsx files/Polym030_Flanker task.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

```


# Data
```{r}
# Merge even and odd data
Even_data <- rbind(Polym001_Flanker_task, Polym002_Flanker_task, Polym004_Flanker_task, Polym006_Flanker_task, Polym008_Flanker_task, Polym010_Flanker_task, Polym012_Flanker_task, Polym014_Flanker_task, Polym016_Flanker_task, Polym018_Flanker_task, Polym020_Flanker_task, Polym022_Flanker_task, Polym024_Flanker_task, Polym026_Flanker_task, Polym028_Flanker_task, Polym030_Flanker_task)

Odd_data <- rbind(Polym003_Flanker_task, Polym005_Flanker_task, Polym007_Flanker_task, Polym009_Flanker_task, Polym011_Flanker_task, Polym013_Flanker_task, Polym015_Flanker_task, Polym017_Flanker_task, Polym019_Flanker_task, Polym021_Flanker_task, Polym023_Flanker_task, Polym025_Flanker_task, Polym027_Flanker_task, Polym029_Flanker_task)


Even_data$key_resp_50_50.rt <- as.numeric(Even_data$key_resp_50_50.rt)
Odd_data$key_resp_50_50.rt <- as.numeric(Odd_data$key_resp_50_50.rt)
Even_data$key_resp_92_8.rt <- as.numeric(Even_data$key_resp_92_8.rt)
Odd_data$key_resp_92_8.rt <- as.numeric(Odd_data$key_resp_92_8.rt)
```

# Keep necessary columns
```{r}
Even_data <- Even_data %>%
  select(participant,condition,corrAns,congruent,key_resp_50_50.keys,key_resp_50_50.corr,key_resp_50_50.rt,key_resp_92_8.keys,key_resp_92_8.corr,key_resp_92_8.rt)

Odd_data <- Odd_data %>%
  select(participant,condition,corrAns,congruent,key_resp_50_50.keys,key_resp_50_50.corr,key_resp_50_50.rt,key_resp_92_8.keys,key_resp_92_8.corr,key_resp_92_8.rt)
```

# Merge data
```{r}
data <- rbind(Even_data, Odd_data)

options(scipen = n)

# Turn response_time into numeric
data$key_resp_50_50.rt <- as.numeric(data$key_resp_50_50.rt)
data$key_resp_92_8.rt <- as.numeric(data$key_resp_92_8.rt)

# Rename columns
data$congruent[data$congruent =="1"] <- "congruent"
data$congruent[data$congruent == "0"] <- "incongruent"
data$condition <- NULL


data <- data %>%
  mutate(response = coalesce(key_resp_50_50.keys,key_resp_92_8.keys)) %>% 
  mutate(correctness = coalesce(key_resp_50_50.corr,key_resp_92_8.corr))%>% 
  mutate(response_time = coalesce(key_resp_50_50.rt,key_resp_92_8.rt)) %>%
  select(participant,corrAns,congruent,response,correctness,response_time)

data <- data %>%
  rename(condition = congruent)

data$correctness[data$correctness == "1"] <- "correct"
data$correctness[data$correctness == "0"] <- "incorrect"
```

```{r}
# Remove practice trials (rows containing NA's)
data <- data %>%
  drop_na()


```

```{r}
# We can calculate the mean reaction times and the error rates for each participant.

options(digits=6)
d_individual_summary <- data %>% 
  group_by(participant) %>%         # calculate the following for each individual
  summarize(mean_RT = mean(response_time),
            error_rate = 1 - mean(ifelse(correctness == "correct", 1, 0)))
  
head(d_individual_summary)


```

# Descriptive statistics
```{r}
library(psych)
describe(data$response_time)
```


```{r}
d_individual_summary %>% 
  ggplot(aes(x = mean_RT, y = error_rate)) +
  geom_point()
```

# Outliers
```{r}
# Identify outliers
d_individual_summary <- d_individual_summary %>% 
  mutate(outlier = case_when(mean_RT < 0.30 ~ TRUE,
                             mean_RT > 0.50 ~ TRUE,
                             error_rate > 0.5 ~ TRUE,
                             TRUE ~ FALSE))
# Plot outliers
d_individual_summary %>% 
  ggplot(aes(x = mean_RT, y = error_rate)) +
  geom_point() +
  geom_point(data = filter(d_individual_summary, outlier == TRUE),
             color = "firebrick", shape = "square", size = 5)


```

```{r}
# We then clean the data set in a first step by removing all participants identified as outliers:

d <- full_join(data, d_individual_summary, by = "participant") # merge the tibbles
d <- filter(d, outlier == FALSE)
message("We excluded ", sum(d_individual_summary$outlier), " participants for suspicious mean RTs and higher error rates.")

#Polym009, Polym020, Polym029 were excluded
```
```{r}

d_sum <- d %>%
  group_by(participant,condition)%>%
  summarise(mean_RT = mean(response_time),
            sd_RT = sd(response_time))
d_sum

```


Numerically, the reaction times for the correct-congruent trials are indeed faster than for the correct-incongruent trials.

Here’s a plot of the reaction times split up by whether the answer was correct and whether the trial was congruent or incongruent.

```{r}
d %>% 
  ggplot(aes(x = response_time)) +
  geom_jitter(aes(y = 0.0005), alpha = 0.1, height = 0.0005) +
  geom_density(fill = "gray", alpha = 0.5) +
  geom_vline(data = d_sum, 
             mapping = aes(xintercept = mean_RT), 
             color = "firebrick") +
  facet_grid(condition ~ correctness)
```


# Accuracy

```{r}
d %>% group_by(condition) %>% 
  summarize(acurracy = mean(correctness == "correct"))
```

Again, numerically it seems that the hypothesis is borne out that accuracy is higher in the congruent trials.



# Performance

Performance will be calculated as the difference in mean reaction times to the incongruent trials and the congruent trials. 



```{r}
congruent <- d %>%
  filter(condition == "congruent")

congruent_mean <- congruent %>% 
  group_by(participant) %>%         
  summarize(mean_congruent = mean(response_time))

incongruent <- d %>%
  filter(condition == "incongruent")

incongruent_mean <- incongruent %>% 
  group_by(participant) %>%         
  summarize(mean_incongruent = mean(response_time))


data3 <- merge(congruent_mean,incongruent_mean,by.x=c("participant"), by.y = c("participant"))

data3 <- data3 %>%
  mutate(performance = mean_incongruent - mean_congruent)

head(data3)
```


```{r}
saveRDS(data3, file = "Flanker_scores.rds", compress = "xz")
```






