---
title: "Analysis of pupil size data"
author: "Maria Polychronidou"
date: "12/3/2022"
output:
  html_document:
    toc: yes
    code_folding: hide
    toc_float:
      collapsed: no
      smooth_scroll: yes
    number_sections: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library("dplyr")
library("mgcv")
library("itsadug")
```
```{r}
memory.limit(size = 1800000)
```


# Load data

```{r}
library(readr)
readRDS("FinalPolym001.rds")
readRDS("FinalPolym002.rds")
readRDS("FinalPolym003.rds")
readRDS("FinalPolym004.rds")
readRDS("FinalPolym005.rds")
readRDS("FinalPolym006.rds")
readRDS("FinalPolym007.rds")
readRDS("FinalPolym008.rds")
readRDS("FinalPolym009.rds")
readRDS("FinalPolym010.rds")
readRDS("FinalPolym011.rds")
readRDS("FinalPolym012.rds")
readRDS("FinalPolym013.rds")
readRDS("FinalPolym014.rds")
readRDS("FinalPolym015.rds")
readRDS("FinalPolym016.rds")
readRDS("FinalPolym017.rds")
readRDS("FinalPolym018.rds")
readRDS("FinalPolym019.rds")
readRDS("FinalPolym020.rds")
readRDS("FinalPolym021.rds")
readRDS("FinalPolym022.rds")
readRDS("FinalPolym023.rds")
readRDS("FinalPolym024.rds")
readRDS("FinalPolym025.rds")
readRDS("FinalPolym026.rds")
readRDS("FinalPolym027.rds")
readRDS("FinalPolym028.rds")
readRDS("FinalPolym029.rds")
readRDS("FinalPolym030.rds")



```

# Merge data

```{r}
require(tidyverse)

rdsfiles <-
  c(
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym001.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym002.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym003.rds", 
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym004.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym005.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym006.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym007.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym008.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym009.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym010.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym011.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym012.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym013.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym014.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym015.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym016.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym017.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym018.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym019.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym020.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym021.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym022.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym023.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym024.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym025.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym026.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym027.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym028.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym029.rds",
    "C:/Users/polyc/Desktop/THESIS/ANALYSIS/PUPIL DATA/FinalPolym030.rds"
    
    
    
    
    
    
  )



data <- rdsfiles %>%
  map_dfr(readRDS)
```



# Delete columns 

```{r}
data$LEFT_ACCELERATION_X <- data$LEFT_ACCELERATION_Y <- data$LEFT_GAZE_X <- data$LEFT_GAZE_Y <- data$LEFT_GAZE_Y <- data$LEFT_IN_BLINK <- data$LEFT_IN_SACCADE <- data$LEFT_PUPIL_SIZE <- data$LEFT_VELOCITY_X <- data$LEFT_VELOCITY_Y <- data$LEFT_VELOCITY_Y <- data$Velocity_X <- data$Velocity_Y <- data$Acceleration_X <- data$Acceleration_Y <- data$Trial_Recycled_ <- data$DATA_FILE <- data$GROUPING_VARIABLES <- data$RIGHT_ACCELERATION_X <- data$RIGHT_ACCELERATION_Y <- data$TARGET_VELOCITY_X <- data$TARGET_VELOCITY_Y <- data$RIGHT_VELOCITY_X <- data$RIGHT_VELOCITY_Y <- data$Pupil_Data <- data$SAMPLE_INDEX <- data$SAMPLE_MESSAGE  <- data$EyeSelected <- NULL
```


# Add cognitive flexibility scores

```{r}
library("readxl")

Language_questionnaire_data <- read_excel("Language questionnaire data.xlsx")
Nback_scores <- readRDS("Nback_scores.rds")
Flanker_scores <- readRDS("Flanker_scores.rds")
Set_shifting_scores <- readRDS("Set-shifting.rds")

data <- merge(data,Nback_scores,by.x=c("Subject"), by.y = c("participant"),all = TRUE)
data <- merge(data,Flanker_scores,by.x=c("Subject"), by.y = c("participant"),all = TRUE)
data <- merge(data, Language_questionnaire_data,by.x=c("Subject"), by.y = c("Participant_number"),all = TRUE)
data <- merge(data, Set_shifting_scores,by.x=c("Subject"), by.y = c("Participant"),all = TRUE)
```


# Keep necessary columns 

```{r}
data <- data %>%
  dplyr::select(Subject, AVERAGE_PUPIL_SIZE, TRIAL_INDEX, RIGHT_GAZE_X, RIGHT_GAZE_Y, RIGHT_INTEREST_AREA_ID, RIGHT_IN_BLINK, RIGHT_IN_SACCADE, RIGHT_PUPIL_SIZE, TIMESTAMP, ACCURACY, condition, critical_word, critical_word_length, criticalword_number, item, syllable_count, Event, CRITICAL_FIX, Time, Pupil, Gaze_X, Gaze_Y, Baseline,aprime,dprime,performance, `Q14_a-f_attitudes`, `Q14_g-t_CLIP-Q`,Q15_social_media,Q16_reading_total,SwitchingCost,MixingCost, logfreq_zipf)

data <- data %>%
  filter(condition != "practice")

data$attitudes <- data$`Q14_a-f_attitudes`
data$CLIP_Q <- data$`Q14_g-t_CLIP-Q`
data$social_media <- data$Q15_social_media
data$reading <- data$Q16_reading_total

```


# Downsample to 50 Hz

```{r}
library(PupilPre)
check_samplingrate(data)
data <- downsample(data, SamplingRate = 250, NewRate = 50) # new sampling rate

```


# Proportional pupil change

```{r}
# New column for the proportional change of pupil according to the baseline of preprocessing 

#The arbitrary pupil units should be transformed into a standardized unit in order to make comparisons between individuals.
#Proportional change relative to baseline (Winn, 2016)

library(tidyverse)

data <- mutate(data, PROPORTIONAL_PUPIL = ((data$RIGHT_PUPIL_SIZE - data$Baseline) / data$Baseline))

# Set values as numeric

data$PROPORTIONAL_PUPIL <- as.numeric(data$PROPORTIONAL_PUPIL)

# Replace Pupil column with proportional pupil change for the steps below (plot etc.)

data$Pupil = data$PROPORTIONAL_PUPIL
```

# Extracting plotting data

```{r}
# Create a list object containing the plotting data.

library(PupilPre)
plt <- ppl_plot_avg(data = data, xlim = c(-200, 3000), Column = "Pupil",
                    Condition1 = "condition", Condition2 = NULL, Cond1Labels = NA,
                    Cond2Labels = NA, Averaging = "Subject", ErrorBar = TRUE,
                    ErrorType = "SE", PupilPreTheme = TRUE) 

df <- plt$data
```

```{r}
# Create a subset with the two critical conditions

data2 <- filter(data, condition == "verb" | condition == "noun")
```


# Plot proportional pupil change 

```{r}
library("ggplot2")
library("PupilPre")

ppl_plot_avg(data = data, xlim = c(-200, 3000), Column = "Pupil", 
             Condition1 = "condition", ErrorBar = TRUE,
                    ErrorType = "SE", PupilPreTheme = FALSE)

```



```{r}
memory.limit(size=900000000)
```
# Baseline model

```{r}
# we use bam because we have a large dataset; bam also contains corrections for autocorrelation

library("mgcv")
model <- bam(Pupil ~ s(Time), data = data2)
summary(model)
```

## Plot model smooths

```{r}
plot(model, rug = F, shade =T, main = "Partial effect", ylab = "Pupil", ylim = c(-0.08,0.08))
plot_smooth(model, view = "Time", rug = F, main = "Full effect",ylim = c(-0.08,0.08))
```
# Model 1

```{r}
# add random effect for subjects
model1 <- bam(Pupil ~ s(Time)
              + s(Subject, bs = 're', m=1),
              data = data2)
summary(model1)
```

## Plot model smooths

```{r}
plot_smooth(model, view = "Time", rug = F, main = "model",ylim = c(-0.08,0.08))
plot_smooth(model1, view = "Time", rug = F, main = "model1",ylim = c(-0.08,0.08)) # we allow variability;that's why we have larger confidence bands
```

## Model comparison
```{r}
model.ml <- bam(Pupil ~ s(Time), data = data2, method = "ML")
model1.ml <- bam(Pupil ~ s(Time) + s(Subject, bs = 're', m=1), data = data2, method = "ML")
compareML(model.ml,model1.ml) # model 1 is better while it has a lower AIC
```


# Model 2 

```{r}
# add factor smooths for subjects and items
model2 <- bam(Pupil ~ s(Time)
              + s(Time, Subject, bs = 'fs', m=1) # add factor smooth instead of random effect
              + s(Time,item,bs="fs", m=1),
              data = data2)
summary(model2)
```

## Plot model smooths

```{r}
plot_smooth(model1, view = "Time", rug = F, main = "model1",ylim = c(-0.08,0.08))
plot_smooth(model2, view = "Time", rug = F, main = "model2",ylim = c(-0.08,0.08))
```

## Model comparison

```{r}
model1.ml <- bam(Pupil ~ s(Time) + s(Subject, bs = 're', m=1), data = data2, method = "ML")
model2.ml <- bam(Pupil ~ s(Time) + s(Time, Subject, bs = 'fs', m=1) + s(Time,item,bs="fs", m=1), data = data2, method = "ML")


compareML(model1.ml,model2.ml) # model 2 is better
```

# Model 3

```{r}
# add fixed effect for condition
data2$condition <- as.factor(data2$condition)
model3 <- bam(Pupil ~ s(Time, by = condition, k=20) + condition
              + s(Time, Subject, bs="fs",m=1) 
              + s(Time,item,bs="fs", m=1), 
              data= data2, discrete= TRUE)
summary(model3)
```

## Plot model smooths

```{r}
plot(model3, rug=F)
abline(h=0)
abline(v=c(0,1000), lty=3)
abline(h=-1*coef(model3)[1],
col='red', lty=2)
```

## Model comparison
```{r}
model2.ml <- bam(Pupil ~ s(Time) + s(Time, Subject, bs = 'fs', m=1) + s(Time,item,bs="fs", m=1), data = data2, method = "ML")
model3.ml <- bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Time, Subject, bs="fs",m=1) + s(Time,item,bs="fs", m=1), data= data2, method = "ML")


compareML(model2.ml,model3.ml) # model 3 is better
```


# Model 4 

```{r}
# add interaction for gaze position
model4 <- bam(Pupil ~ s(Time, by = condition, k=20) + condition
              + s(Gaze_X, Gaze_Y) 
              + s(Time, Subject, bs="fs",m=1) 
              + s(Time,item,bs="fs", m=1), 
              data= data2, discrete= TRUE)
summary(model4)
```

## Plot model smooths

```{r}
plot(model4, rug=F)
abline(h=0)
abline(v=c(0,1000), lty=3)
abline(h=-1*coef(model4)[1],
col='red', lty=2)
```

## Model comparison

```{r}
model3.ml <- bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Time, Subject, bs="fs",m=1) + s(Time,item,bs="fs", m=1), data= data2, method = "ML")
model4.ml <-bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y) + s(Time, Subject, bs="fs",m=1) + s(Time,item,bs="fs", m=1), data= data2, method = "ML")

compareML(model3.ml,model4.ml) # model 4 is better

```


# Model 5

```{r}
# add fixed effect for N-back scores and exclude random smooth for items
model5 <- bam (Pupil ~ s(Time, by = condition, k=20) 
               + condition 
               + s(Gaze_X, Gaze_Y)
               + s(Time, by = aprime, k=20)
               + s(Time, Subject, bs="fs",m=1), 
               data= data2,discrete= TRUE)
 summary(model5) 
```

## Plot model smooths

```{r}
plot(model5, rug=F)
abline(h=0)
abline(v=c(0,1000), lty=3)
abline(h=-1*coef(model5)[1],
col='red', lty=2)
```

## Model comparison
```{r}
model4.ml <- bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y) + s(Time, Subject, bs="fs",m=1) + s(Time,item,bs="fs", m=1), data= data2, method = "ML")
model5.ml <- bam (Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y)+ s(Time, by = aprime, k=20) + s(Time, Subject, bs="fs",m=1), data= data2, method = "ML")

compareML(model4.ml,model5.ml) # model 4 is better
```


# Model 6

```{r}
# add fixed effect for Flanker task scores

model6 <- bam (Pupil ~ s(Time, by = condition, k=20) 
               + condition 
               + s(Gaze_X, Gaze_Y)
               + s(Time, by = performance, k=20)
               + s(Time, Subject, bs="fs",m=1), 
               data= data2,discrete= TRUE)
 summary(model6) 
```

## Plot model smooths

```{r}
plot(model6, rug=F)
abline(h=0)
abline(v=c(0,1000), lty=3)
abline(h=-1*coef(model6)[1],
col='red', lty=2)
```
```{r}
library(mgcv)
library(itsadug)
```


## Model comparison
```{r}
model4.ml <- bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y) + s(Time, Subject, bs="fs",m=1) + s(Time,item,bs="fs", m=1), data= data2, method = "ML")
model6.ml <- bam (Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y) + s(Time, by = performance, k=20) + s(Time, Subject, bs="fs",m=1), data= data2, method = "ML")

compareML(model4.ml,model6.ml) # model 4 is better
```



# Model 7

```{r}
# add fixed effect for set-shifting task scores

model7 <- bam(Pupil ~ s(Time, by = condition, k=20) 
              + condition  
              + s(Gaze_X, Gaze_Y)
              + s(Time, by = MixingCost, k=20)
              + s(Time, Subject, bs="fs",m=1), 
              data= data2, discrete= TRUE)
summary(model7)
```

## Plot model smooths

```{r}
plot(model7, rug=F)
abline(h=0)
abline(v=c(0,1000), lty=3)
abline(h=-1*coef(model7)[1],
col='red', lty=2)
```





## Model comparison
```{r}
model4.ml <- bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y) + s(Time, Subject, bs="fs",m=1) + s(Time,item,bs="fs", m=1), data= data2, method = "ML")
model7.ml <- bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y) + s(Time, by = MixingCost, k=20) + s(Time, Subject, bs="fs",m=1), data= data2, method = "ML")

compareML(model4.ml,model7.ml) # model 4 is better
```


# Model 8

```{r}
# add fixed effect for attitudes

model8 <- bam(Pupil ~ s(Time, by = condition, k=20) 
              + condition
              + s(Gaze_X, Gaze_Y)
              + s(Time, by = attitudes, k=20)
              + s(Time, Subject, bs="fs",m=1), 
              data= data2, discrete= TRUE)
summary(model8)
```



## Plot model smooths

```{r}
plot(model8, rug=F)
abline(h=0)
abline(v=c(0,1000), lty=3)
abline(h=-1*coef(model8)[1],
col='red', lty=2)
```


## Model comparison
```{r}
model4.ml <- bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y) + s(Time, Subject, bs="fs",m=1) + s(Time,item,bs="fs", m=1), data= data2, method = "ML")
model8.ml <- bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y) + s(Time, by = attitudes, k=20) + s(Time, Subject, bs="fs",m=1), data= data2, method = "ML")

compareML(model4.ml,model8.ml) # model 4 is better
```



# Model 9

```{r}
# add fixed effect for CLIP_Q

model9 <- bam(Pupil ~ s(Time, by = condition, k=20) 
              + condition  
              + s(Gaze_X, Gaze_Y)
              + s(Time, by = CLIP_Q, k=20)
              + s(Time, Subject, bs="fs",m=1), 
              data= data2, discrete= TRUE)
summary(model9)
```



## Plot model smooths

```{r}
plot(model9, rug=F)
abline(h=0)
abline(v=c(0,1000), lty=3)
abline(h=-1*coef(model9)[1],
col='red', lty=2)
```


## Model comparison
```{r}
model4.ml <- bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y) + s(Time, Subject, bs="fs",m=1) + s(Time,item,bs="fs", m=1), data= data2, method = "ML")
model9.ml <- bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y) + s(Time, by = CLIP_Q, k=20) + s(Time, Subject, bs="fs",m=1), data= data2, method = "ML")

compareML(model4.ml,model9.ml) # model 4 is better
```

# Model 10

```{r}
# add fixed effect for reading habits

model10 <- bam(Pupil ~ s(Time, by = condition, k=20) 
              + condition  
              + s(Gaze_X, Gaze_Y)
              + s(Time, by = reading, k=20)
              + s(Time, Subject, bs="fs",m=1), 
              data= data2, discrete= TRUE)
summary(model10)
```



## Plot model smooths

```{r}
plot(model10, rug=F)
abline(h=0)
abline(v=c(0,1000), lty=3)
abline(h=-1*coef(model10)[1],
col='red', lty=2)
```


## Model comparison
```{r}
model4.ml <- bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y) + s(Time, Subject, bs="fs",m=1) + s(Time,item,bs="fs", m=1), data= data2, method = "ML")
model10.ml <- bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y) + s(Time, by = reading, k=20) + s(Time, Subject, bs="fs",m=1), data= data2, method = "ML")

compareML(model4.ml,model10.ml) # model 4 is better
```



# Model 11

```{r}
# add fixed effect for social media use

model11 <- bam(Pupil ~ s(Time, by = condition, k=20) 
              + condition  
              + s(Gaze_X, Gaze_Y)
              + s(Time, by = social_media, k=20)
              + s(Time, Subject, bs="fs",m=1), 
              data= data2, discrete= TRUE)
summary(model11)
```



## Plot model smooths

```{r}
plot(model11, rug=F)
abline(h=0)
abline(v=c(0,1000), lty=3)
abline(h=-1*coef(model11)[1],
col='red', lty=2)
```


## Model comparison
```{r}
model4.ml <- bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y) + s(Time, Subject, bs="fs",m=1) + s(Time,item,bs="fs", m=1), data= data2, method = "ML")
model11.ml <- bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y) + s(Time, by = social_media, k=20) + s(Time, Subject, bs="fs",m=1), data= data2, method = "ML")

compareML(model4.ml,model11.ml) # model 4 is better
```



# Model criticism

## Check residuals

To evaluate the model fit, we look at the residuals.

```{r}
gam.check(model4)

```

The first plot shows that the residuals deviate from the straight line.
In addition, the plot with the response and fitted values confirms the high autocorrelation.



## Check autocorrelation

```{r}
acf(resid(model4), main='ACF of res model4')
```

Again the residuals plot shows high autocorrelation (there are high values for Lag 1 and following lags).


# Correcting for autocorrelation

## Create new model

```{r}
rho=0.99 # use the amount of correlation at lag 2
model4_corr <- bam(Pupil ~ s(Time, by = condition, k=20) 
                   + condition 
                   + s(Gaze_X, Gaze_Y) 
                   + s(Time, Subject, bs="fs",m=1) 
                   + s(Time,item,bs="fs", m=1), data= data2, rho=rho)

summary(model4_corr)
```
## Plot residuals of the two models

```{r}
# autocorrelation has been removed
par(mfrow = c(1,2))
acf_resid(model4, main = "ACF of model 4")
acf_resid(model4_corr, main = "ACF of corrected model4")

```
## Compare the two models

```{r}
model4.ml <- bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y) + s(Time, Subject, bs="fs",m=1) + s(Time,item,bs="fs", m=1), data= data2, method = "ML")
model4_corr <- bam(Pupil ~ s(Time, by = condition, k=20) + condition + s(Gaze_X, Gaze_Y) + s(Time, Subject, bs="fs",m=1) + s(Time,item,bs="fs", m=1), data= data2, rho=rho, method = "ML")

compareML(model4.ml, model4_corr) # clear model improvement, model4_corr has lower AIC
```

# Plot model smooths of the best-fitting model

```{r}
plot(model4_corr, rug=F)
abline(h=0)
abline(v=c(0,1000), lty=3)
abline(h=-1*coef(model4_corr)[1],
col='red', lty=2)
```
# Visualizing the patterns of the best-fitting model

```{r}
plot_smooth(model4_corr, view = "Time", rug = F, plot_all = "condition", main = "Best-fitting model")

```

```{r}
par(mfrow=c(1,1), cex=1.1)
# including random effects:
fvisgam(model4_corr, view=c("Gaze_X","Gaze_Y"), cond=list(Group="verb"))
```

















